---
title: "PP4H SDoH Food Equity Program Evaluation"
author: "PP4H"
date: "4/2/2021"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

BaselineData_2019_maywood <- BaselineData_2019_geom %>% st_drop_geometry()

write_clip(BaselineData_2019_maywood)
write_clip(vitalstatistics_Maywood)


# import tables
produce_donations <- read_excel("../data/PP4H_ScaleData.xlsx", sheet="produce_donations") %>%
  mutate(year=format(as.Date(as.character(year), "%Y"),"%Y"),
         month=format(as.Date(month, "%B"), "%B"))




```

## Project Description

Proviso Partners for Health is undertaking a systematic evaluation of its food equity programs.

The evaluation is supported by the Center for Disease Control (CDC) for the purpose of informing CDC, NACCHO, and ASTHO about the barriers and opportunities associated with  multisector coalitions.

Resources: 
<http://rmarkdown.rstudio.com>
<https://www.provisopartners.com>

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

